Effects of bariatric surgery and weight loss on resting state functional connectivity

### 2021-01-07 manuscript/draft_rsfmri.Rmd

@@

```
<!-- STUDY PROCEDURE --> Subjects arrived in the morning (between 07:00 and 12:00) after an overnight fast. They underwent medical assessments including an interview, blood draw and anthropometric measurements before having a one our break for <!-- standadized??  -->breakfast. MRI scanning was done after further psychological tests (for details see @Prehn_2020).
```{r figBMIdescr, fig.align='center', out.width="90%", fig.cap="BMI over time.", echo=FALSE}
# eval = TRUE, fig.asp = 0.7, fig.width = 6
source("report/figures.R")
fig_BMIdescr <- mk_figBMIdescr(final)
fig_BMIdescr
```

@@

#### with adjustment for age, sex, meanFD
There was no interaction of group and time point regarding the resting state connectivity for neither the PCC nor the NAcc as was hypothesized. Nor was there a significant main effect for any of the covariates of interest (time, group) in clusterwise inference with FWE correction.

#### with adjustment for age and sex
Similarly, there were only non-findings when reducing the number of nuisance covariates by leaving out mean FD. Results did not differ between analyses of connectivity maps from different preprocessing pipelines.
<!-- There was no other significant co-activation for any other region of interest for neither of the preprocessing variants. -->

@@

In our sample, extend of micromovements of the head averaged across all measurements is associated with increased functional connectivity between reward and frontal regions. <!-- explanation? overlap with region from change in BMI? -->

>>>>

\newpage
# Abstract

\newpage
# Introduction

@@

```
<!-- STUDY PROCEDURE --> Subjects arrived in the morning (between 07:00 and 12:00) after an overnight fast. They underwent medical assessments including an interview, blood draw and anthropometric measurements before having a one our break for <!-- standadized??  -->breakfast. MRI scanning was done after further psychological tests (for details see @Prehn_2020).
```{r figBMIdescr, fig.align='center', out.width="90%", fig.cap="BMI over time.", echo=FALSE}
# eval = TRUE, fig.asp = 0.7, fig.width = 6
source("report/figures.R")

fig_BMIdescr <- mk_figBMIdescr(final)
fig_BMIdescr

@@

#### with adjustment for age, sex, meanFD

<!-- Brain mask: Group*Time Interaction [CORRECTED] -->
There was no interaction of group and time point regarding the resting state connectivity for neither the PCC nor the NAcc seeds against our initial hypothesis. There also was no significant main effect for any of the covariates of interest (time, group) in clusterwise inference with FWE correction.

#### with adjustment for age and sex
Similarly, there were no significant clusters when leaving out mean FD. Results did not differ between AROMA+CC and AROMA+CC+GSR preprocessing pipelines.

<!-- There was no other significant co-activation for any other region of interest for neither of the preprocessing variants. -->

@@

# Discussion
In our sample, extend of micromovements of the head averaged across all measurements is associated with increased functional connectivity between reward and frontal regions. <!-- explanation? overlap with region from change in BMI? -->
